Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-04-09 journal-draft/bare_jrnl_comsoc.tex
modified proof for T5.1

Given a finite set $\mathcal{G} = \{ g_1, \ldots , g_N \} \subsetneq \mathbb{N}$ of non-negative integers and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ such that $S_i \subseteq \mathcal{G}$ for every $1 \leq i \leq N$.
Each set $S \in \mathcal{Q}$ is associated with a weight $w(S) \in \mathbb{R}$.
Further, we are given a threshold value $\lambda \in \mathbb{N}$.\\
The question is whether there exists a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets, i.e., for all $S, S' \in \mathcal{S}$ with $S \neq S'$ it holds that $S \cap S' = \emptyset$, and the total weight of the sets in $\mathcal{S}$ is greater than $\lambda$, i.e., $\sum_{S \in \mathcal{S}} w(S) > \lambda$.
\end{mydef}

@@

To prove that the centralized clustering problem is NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to prove the former is at least as hard as the latter.
%, which means centralized clustering in CRN problem is as hard as weighted k-set packing to be solved.
%To complete the reduction, we need to conduct following two steps:
%\begin{itemize}
%\item Step 1: We show the existence a polynomial algorithm $\sigma$, by which any instance $\mathcal{S}$ of a weighted k-set packing can be transformed to a clustering solution $\sigma(\mathcal{S})$ which complies with Definition~\ref{def_centralized_clustering}.
%\item Step 2: Show that $\mathcal{S}$ is a \textit{yes} instance of weighted k-set packing if and only if $\sigma(\mathcal{S})$ is a \textit{yes} instance for CRN clustering problem.
%\end{itemize}
We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{S}$ (COMMENT: be careful - there is an overloading of $\mathcal{S}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{S})$) of centralized clustering such that ... (to be completed - Erwin can do that)

%We continue to use the notation adopted in the problem definition in Section~\ref{centralized_opt}.
W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
%$\mathcal{Q}$ is a collection of sets $\{s_1, s_2,\cdots s_m\}$, each set is composed with certain elements in $\mathcal{G}$. REPEATING THE DEF??
%Assume $\mathcal{S}\subseteq \mathcal{Q}$ is one instance of weighted k-set packing, and the sets in $\mathcal{S}$ are disjoint.
%$\omega$ indicates the weight for each set $s$, $\omega:\mathcal{S}\rightarrow \mathbb{Z}^{+}$. COMMENT: again unnecessary. Already contained in the definition!
%As the number of common channel of clusters is always integer
%give new weight to them in following way

ERWIN FINISHED HERE FOR THE MOMENT ---

The polynomial algorithm $\sigma$ consists of three transformations.

\begin{itemize}
\item Given a collection $\mathcal{Q}$, on basis of which we construct a CRN. (I DON'T UNDERSTAND THAT. What do you mean?)
%We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
We regard each set in $\mathcal{Q}$ as a cluster, whose number of CCCs is equal to the weight of that set.

%There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively. (THAT'S TOO HAND-WAVY.)
%Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
We find it is impossible to map the sets into clusters in the same time (SORRY, which sets?? The sets you mentioned before are already clusters, isn't it?), because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
(THIS PARAGRAPH IS TOO DIFFICULT FOR ME TO UNDERSTAND.)

\item In the second step, we transform the instance $\mathcal{S}$ to $\mathcal{S'}$ by adding dummy elements into each set in $\mathcal{S}$.
Formally, for each set $s_i\in \mathcal{S}$, we create $s_i' = s_i \times \{ 1,2\}$. %for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1',4,4',6,6' \}$.
%By doing this, we obtain the dummy sets and constitute the dummy instance $\mathcal{S}'$ based on $\mathcal{S}$.
The purpose of this transformation is to eliminate the set in $\mathcal{S}$, which has single element.
The weight of these sets remain unchanged, \ie $\omega(s_i)=\omega(s_i')$.
%After this transmission, there is no set with only one element.
%This transformation requires $\sum_{s_i \in \mathcal{S}} |s_i|$ steps.

\item In this step, we transform the instance $\mathcal{S'}$ to a clustering solution for CRN.
We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
We locate these CR nodes besides the CR nodes with the same IDs (THAT DOESN'T MAKE SENSE. THEN THE ID IS NOT UNIQUE ANYMORE.) in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node). (YOU DON'T NEED TO GIVE PRACTICAL MOTIVATION IN A HARDNESS-PROOF.)
Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{S'}$ doesn't have singleton cluster.
This transformation requires $2\cdot\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
%
Afterwards, the CR node whose ID doesn't appear in any set in $\mathcal{S}$ becomes single node clusters, according to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
These singleton clusters and the clusters in $\mathcal{S}$ constitute a clustering solution, and finding the singleton clusters requires at most $N$ steps.
%We deliberately locate them so that at least one CR node can communicate with the rest of them.
%map every element in $\mathcal{S}$ into one CR node, \ie each integer corresponds to one CR node, in particular, that integer becomes the CR node's ID.
%As $s'$ is dummy set which has duplicated elements, we also deploy the the same CR node twice.
%
An example is shown in Table~\ref{no_hard_proof_instance}.
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{ p{3cm}  p{4.5cm} }
     \toprule
      $\mathcal{N}$  & $\{1,2,3,4,5\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      Instance for Weighted k-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      Instance with dummy elements
      & 
		$\{ \, \{(1,1),(1,2)\},\{(2,1),(2,2),$ \\ &$(3,1),(3,2) \}, \{ (4,1), (4,2) \} \, \}$
      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
	Instance for clustering solution (dashed circles are dummy nodes)
	  &
	  %\raisebox{-\totalheight}{\includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}}      
	  \begin{minipage}{.3\textwidth}
      \includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}
    \end{minipage}
	  \\       \bottomrule
      \end{tabular}
      \caption{}
      \label{no_hard_proof_instance}
      \end{center}
      \end{table}

@@

We have crossed the hurdle of finding one polynomial algorithm $\sigma$ which transforms an instance of weighted k-set packing to an instance of the clustering problem in CRN.
Now we look into the step 2 in the reduction.
As to an instance $\mathcal{S}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{S'}$, even $\mathcal{S}$ contains set which only has one element.
Thus, when the instance $\mathcal{S}$ is one solution and its sum weights is greater than $\lambda$, in the CRN which is mapped from $\mathcal{S'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
%
When there is no solution out of set $\mathcal{G}$ for weighted k-set packing,
%let's assume the maximum sum of weights of all instances is $\sum_{s_i\in \mathcal{S}}\omega(s_i)=\delta < \lambda$. 
%The dummy set of each $s_i\in \mathcal{S}$ is mapped to cluster of CR nodes.
%Definition of CRN clustering regulates that the number of common channels is 0 when the cluster has only one node.
%As to $|s_i|=1$, the mapped cluster has two nodes, with one of them is the dummy CR node.
%Then number of common channels is on longer 0 but equals to the weight of corresponding set $s_i$.
%%Meanwhile, the number of common channels of all the other single node cluster is 0.
the summed number of CCCs of the clusters in the mapped CRN is also smaller than $\lambda$.

>>>>

Given a finite set $\mathcal{G} = \{ g_1, \ldots , g_N \} \subsetneq \mathbb{N}$ of non-negative integers and a collection of sets $\mathcal{Q}=\{S_1,S_2,\cdots,S_m\}$ such that $S_i \subseteq \mathcal{G}$ for every $1 \leq i \leq N$.
Each set $S \in \mathcal{Q}$ is associated with a weight $\omega(S) \in \mathbb{R}$.
Further, we are given a threshold value $\lambda \in \mathbb{N}$.\\
The question is whether there exists a collection $\mathcal{S} \subseteq \mathcal{Q}$ such that $\mathcal{S}$ contains only pairwise disjoint sets, i.e., for all $S, S' \in \mathcal{S}$ with $S \neq S'$ it holds that $S \cap S' = \emptyset$, and the total weight of the sets in $\mathcal{S}$ is greater than $\lambda$, i.e., $\sum_{S \in \mathcal{S}} \omega(S) > \lambda$.
\end{mydef}

@@

To prove that the centralized clustering problem is NP-hard, we reduce the NP-hard problem \textit{weighted k-set packing} to it to prove the former is at least as hard as the latter.
%, which means centralized clustering in CRN problem is as hard as weighted k-set packing to be solved.
%To complete the reduction, we need to conduct following two steps:
%\begin{itemize}
%\item Step 1: We show the existence a polynomial algorithm $\sigma$, by which any instance $\mathcal{S}$ of a weighted k-set packing can be transformed to a clustering solution $\sigma(\mathcal{S})$ which complies with Definition~\ref{def_centralized_clustering}.
%\item Step 2: Show that $\mathcal{S}$ is a \textit{yes} instance of weighted k-set packing if and only if $\sigma(\mathcal{S})$ is a \textit{yes} instance for CRN clustering problem.
%\end{itemize}
We show the existence of a polynomial-time algorithm $\sigma$ that transforms any instance $\mathcal{I}$ of a weighted $k$-set packing into an instance $\sigma(\mathcal{S})$) of centralized clustering problem.

%We continue to use the notation adopted in the problem definition in Section~\ref{centralized_opt}.
W.l.o.g. let set $\mathcal{G} = \{ 1, \ldots , N \}$.
%$\mathcal{Q}$ is a collection of sets $\{s_1, s_2,\cdots s_m\}$, each set is composed with certain elements in $\mathcal{G}$. REPEATING THE DEF??
%Assume $\mathcal{S}\subseteq \mathcal{Q}$ is one instance of weighted k-set packing, and the sets in $\mathcal{S}$ are disjoint.
%$\omega$ indicates the weight for each set $s$, $\omega:\mathcal{S}\rightarrow \mathbb{Z}^{+}$. COMMENT: again unnecessary. Already contained in the definition!
%As the number of common channel of clusters is always integer
%give new weight to them in following way
The polynomial algorithm $\sigma$ consists of three steps.

\begin{itemize}

\item In the first step, we transform the instance $\mathcal{I}$ to $\mathcal{I'}$ by adding dummy elements into each set in $\mathcal{I}$.
Formally, for each set $s_i\in \mathcal{I}$, we create $s_i' = s_i \times \{ 1,2\}$.
Then we change the dummy elements by adding $N$ on them.
 %for instance, given $s_i=\{1, 4, 6\}$, the dummy set $s_i'$ is $\{1,1',4,4',6,6' \}$.
%By doing this, we obtain the dummy sets and constitute the dummy instance $\mathcal{S}'$ based on $\mathcal{S}$.
The purpose of this transformation is to eliminate the set in $\mathcal{I}$, which has single element.
The weight of these sets remain unchanged, \ie $\omega(s_i') = \omega(s_i)$.
%After this transmission, there is no set with only one element.
%This transformation requires $\sum_{s_i \in \mathcal{S}} |s_i|$ steps.

\item Mapping the elements in $\mathcal{I'}$ to CR nodes, and mapping the sets in $\mathcal{I'}$ to clusters.
There is a bijection between the union of sets in $\mathcal{I'}$ to the CRN which consists of the CR nodes, in particular, each element one-to-one corresponds to the CR node whose node ID equals to the element.
%Given a collection $\mathcal{Q}$, on basis of which we construct a CRN. (I DON'T UNDERSTAND THAT. What do you mean?)
%We prepare $N$ CR nodes who are labelled from 1 to $N$, put them on a 2 dimension space, and deem a pair of them can communicate if they appear in one same set in $\mathcal{Q}$.
%We define a set of CR nodes $\mathcal{N} = \{ 1, \ldots , N \}$
We further regulate that, each set in $\mathcal{I}$ as a corresponding cluster, \ie there is a bijection between a set in $\mathcal{I}$ and a set of node IDs in a cluster, besides, the number of CCCs is equal to the weight of the corresponding set.

%%There is one situation deserving extra explanation in the second transformation, we adopt one example to discuss it.
%Assuming two sets in $\mathcal{Q}$ are $s_1=\{1,2\}$ and $s_2=\{1,2,3\}$, then their weights are 3 and 5 respectively. (THAT'S TOO HAND-WAVY.)
%%Their dummy sets are $s_1'=\{1,1,2,2\}$ and $s_2'=\{1,1,2,2,3,3,4,4\}$ and their new weights are 3 and 5 as before.
%We find it is impossible to map the sets into clusters in the same time (SORRY, which sets?? The sets you mentioned before are already clusters, isn't it?), because the number of CCCs of the cluster which bases on $s_1$ should be no less than the cluster which bases on $s_2$, as the latter has one extra node compared with the former cluster.
%%When $s_1'$ and $s_2'$ are mapped to CRN respectively, there is contradiction between them, because the number of common channels of CR node group $\{1,1,2,2\}$ is smaller than that of $\{1,1,2,2,3,3,4,4\}$.
%But as to any instance of the solution to the weighted k-set packing problem, this contradiction doesn't happen because the instance $\mathcal{S}$ contains only disjoint sets, thus at most only one set of $s_1$ and $s_2$ appears in $\mathcal{S}$.%, then we can safely delete the connections based on the deleted set from the CRN, and the contradiction is eliminated.
%(THIS PARAGRAPH IS TOO DIFFICULT FOR ME TO UNDERSTAND.)

\item In this step, we transform the instance $\mathcal{I'}$ to a clustering proposal for CRN.
%We prepare a second pool of CR nodes which are identical with the CR nodes prepared in step 1, i.e., identical IDs and channel availabilities on them, we call these CR nodes dummy nodes.
We adjust the locations of the CR nodes which are mapped from the dummy elements in the instance $\mathcal{I'}$, to let them beside the CR nodes whose ID is $N$ smaller.
% (THAT DOESN'T MAKE SENSE. THEN THE ID IS NOT UNIQUE ANYMORE.) in the CRN built in step 1, and there is connection between the CR node and its dummy node (the one CR node and its dummy node can be seen as two transceivers at one node). (YOU DON'T NEED TO GIVE PRACTICAL MOTIVATION IN A HARDNESS-PROOF.)
Because of the dummy nodes, the clustering solution which corresponds to $\mathcal{S'}$ doesn't have singleton cluster.
This transformation requires $2\cdot\sum_{s_i \in \mathcal{S}} |s_i|$ steps.
%
Afterwards, the CR node whose ID is smaller than $N$ and doesn't appear in any set in $\mathcal{S}$ becomes single node clusters, according to the definition of clustering problem in CRN, the number of CCCs in these single node clusters is 0.
These singleton clusters and the clusters in $\mathcal{S}$ constitute a clustering proposal, and finding these singleton clusters requires at most $N$ steps.
%We deliberately locate them so that at least one CR node can communicate with the rest of them.
%map every element in $\mathcal{S}$ into one CR node, \ie each integer corresponds to one CR node, in particular, that integer becomes the CR node's ID.
%As $s'$ is dummy set which has duplicated elements, we also deploy the the same CR node twice.
%
An example is shown in Table~\ref{no_hard_proof_instance}.
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{ p{3cm}  p{4.5cm} }
     \toprule
      $\mathcal{N}$  & $\{0, 1,2,3,4,5,6, 7, 8, 9\}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      $\mathcal{Q}$  & $\{ \{1\}, \{1, 5\}, \{1,2,4\}, \{2,3\}, \{4\} \}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}     
      Instance for Weighted k-set packing  & $\{ \{1\}, \{2,3\}, \{4\} \}$\\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      Instance with dummy elements
      & 
		$\{ \, \{1,11\},\{2,12, 3, 13\}, \{ 4,14\} \, \}$
      \\    \cmidrule(r){1-1}\cmidrule(lr){2-2}
	Instance for clustering solution (dashed circles are dummy nodes)
	  &
	  %\raisebox{-\totalheight}{\includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}}      
	  \begin{minipage}{.3\textwidth}
      \includegraphics[width=0.8\linewidth]{np_hard_proof_dummy.pdf}
    \end{minipage}
	  \\       \bottomrule
      \end{tabular}
      \caption{}
      \label{no_hard_proof_instance}
      \end{center}
      \end{table}

@@

We have crossed the hurdle of finding one polynomial algorithm $\sigma$ which transforms an instance of weighted k-set packing to an instance of the clustering problem in CRN.
%Now we look into the step 2 in the reduction.
As to an instance $\mathcal{I}$ for weighted k-set packing, the sum weights is identical to the sum of CCCs in the CRN mapped from $\mathcal{I'}$, even $\mathcal{I}$ contains set which only has one element.
Thus, when the instance $\mathcal{S}$ is one solution and its sum weights is greater than $\lambda$, in the CRN which is mapped from $\mathcal{S'}$, the summed number of CCCs of the clusters is greater than $\lambda$.
When there is no solution out of set $\mathcal{G}$ for weighted k-set packing,
%let's assume the maximum sum of weights of all instances is $\sum_{s_i\in \mathcal{S}}\omega(s_i)=\delta < \lambda$. 
%The dummy set of each $s_i\in \mathcal{S}$ is mapped to cluster of CR nodes.
%Definition of CRN clustering regulates that the number of common channels is 0 when the cluster has only one node.
%As to $|s_i|=1$, the mapped cluster has two nodes, with one of them is the dummy CR node.
%Then number of common channels is on longer 0 but equals to the weight of corresponding set $s_i$.
%%Meanwhile, the number of common channels of all the other single node cluster is 0.
the summed number of CCCs of the clusters in the mapped CRN is also smaller than $\lambda$.

When an instance $\mathcal{I}$ contains joint sets, there will be overlapped clusters among the mapped clusters, then neither is solution to their corresponding problem.
